### 2018-12-17 README.Rmd
start working on areal vignette

`areal` offers an intuitive toolkit for validating and interpolating spatial data. Areal interpolations is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons - is the lack of easy to use tools for completing the processes. While methods for implementing various areal interpolation approaches are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`. `areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well. This will be posted on the package's website before the initial CRAN release.

>>>>

`areal` offers an intuitive toolkit for validating and interpolating spatial data. Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons - is the lack of easy to use tools for completing the processes. While methods for implementing various areal interpolation approaches are available outside of the `R` ecosystem (ex - toolboxes in ArcGIS) and within `R` (the `sf` package's `st_interpolate_aw`) function, `areal` fills a niche by providing additional functionality not available in `sf` while taking advantage of the reproducibility of `R`. `areal` currently implents only areal weighted interpolation, but a roadmap is being developed to add additional interpolation methods as well. This will be posted on the package's website before the initial CRAN release.
